Compositional Quantitative Resource Analysis of C Programs

### 2014-06-21 paper/main.tex
uniformize forall notations

\begin{figure}
\center
\begin{minipage}[b]{0.8\linewidth}
\begin{lstlisting}
${\color{blue}%
  \{ \#_1(a) + 2k \}}$
while (k > 0) {
  ${\color{blue}%
    \{ \#_1(a) + 2k \}}$
  while (x < N && a[x] == 1) {
    ${\color{blue}%
      \{ (a[x] = 1) + \#_1(a) + 2k \}}$
    a[x]=0;
    ${\color{blue}%
      \{ \#_1(a) + 2k + 1 \}}$
    tick(1);
    ${\color{blue}%
      \{ \#_1(a) + 2k \}}$
    x++; }
  ${\color{blue}%
    \{ (x \ge N \lor a[x] = 0) + \#_1(a) + 2k \}}$
  if (x < N) {
    ${\color{blue}%
      \{ (a[x] = 0) + \#_1(a) + 1 + 2(k-1) + 1 \}}$
    a[x]=1;
    ${\color{blue}%
      \{ \#_1(a) + 2(k-1) + 1 \}}$
    tick(1); }
  ${\color{blue}%
    \{ \#_1(a) + 2(k-1) \}}$
  k--;
  ${\color{blue}%
    \{ \#_1(a) + 2k \}}$
} ${\color{blue} \{ \#_1(a) \}}$

\end{lstlisting}
\end{minipage}

\caption{Exemple derivation using amortized reasoning, we noted
  $\#_1(a)$ for $\# \{ i \mid 0 \le i < N \land a[i] = 1 \}$, we use the
  tick metric that assigns cost $n$ to \lstinline{tick(n)} statements and
  0 to other operations.
  }
\label{fig:xmplinc}
\end{figure}

\begin{figure}
\begin{lstlisting}
${\color{blue}%
  \{ (Z = \log_2(h-l)) + Z \} }$
bsearch(x,l,h) {
  if (h-l > 1) {
    ${\color{blue}%
      \{ (h-l > 1 \land Z = \log_2(h-l)) + Z \} }$
    m = h + (h-l)/2;
    ${\color{blue}%
      \{ (m = \frac{h+l}{2} \land h-l > 1 \land Z = \log_2(h-l)) + Z \} }$
    if (a[m]>x) h=m; else l=m;
    ${\color{blue}%
      \{ (Z - 1 = \log_2(h-l)) + (Z-1) + 1 \} }$
    l = bsearch(x,l,h); }
  ${\color{blue}%
    \{ Z-1 \} }$
  return l;
} ${\color{blue} \{ Z \} }$
\end{lstlisting}
\caption{Exemple derivation of a stack usage bound for a binary
  search program, the metric used assigns a cost of 1 to function
  calls and $-1$ to return statements, we noted $Z$ an arbitrary
  logical variable.
  }
\end{figure}

>>>>

\begin{figure}
\begin{lstlisting}
${\color{blue}%
  \{ \#_1(a) + 2k \}}$
while (k > 0) {
  ${\color{blue}%
    \{ \#_1(a) + 2k \}}$
  while (a[x] == 1 && x < N) {
    ${\color{blue}%
      \{ (a[x] = 1) + \#_1(a) + 2k \}}$
    a[x]=0;
    ${\color{blue}%
      \{ (a[x] = 0) + \#_1(a) + 2k + 1 \}}$
    tick(1);
    ${\color{blue}%
      \{ \#_1(a) + 2k \}}$
    x++; }
  ${\color{blue}%
    \{ \#_1(a) + 2k \}}$
  if (x < N) {
    ${\color{blue}%
      \{ \#_1(a) + 1 + 2(k-1) + 1 \}}$
    a[x]=1;
    ${\color{blue}%
      \{ \#_1(a) + 2(k-1) + 1 \}}$
    tick(1); }
  ${\color{blue}%
    \{ \#_1(a) + 2(k-1) \}}$
  k--;
  ${\color{blue}%
    \{ \#_1(a) + 2k \}}$
} ${\color{blue} \{ 0 \}}$

\end{lstlisting}
\caption{Exemple derivation using amortized reasoning, we noted
  $\#_1(a)$ for $\# \{ i \mid 0 \le i < N \land a[i] = 1 \}$, we use the
  tick metric that assigns cost $n$ to \lstinline{tick(n)} statments and
  0 to other operations.
  }
\label{fig:xmplinc}
\end{figure}
